Security of deployed Android devices

### 2014-01-13 netos2014-01-14.tex
Add a couple of graphs on wifi networks to the end of the netos talk

>>>>

\begin{frame}[plain]{Connections to secured wifi networks}{}
 \pgfdeclareimage[height=0.95\textheight]{wifi-accounts-stotals}{figures/wifi-accounts-stotals-hist}
 \begin{center}
  \vspace{-0.2em}
  \hspace{-3em}\pgfuseimage{wifi-accounts-stotals}
 \end{center}
\end{frame}
\begin{frame}[plain]{Connections to open wifi networks}{}
 \pgfdeclareimage[height=0.95\textheight]{wifi-accounts-ototals}{figures/wifi-accounts-ototals-hist}
 \begin{center}
  \vspace{-0.2em}
  \hspace{-3em}\pgfuseimage{wifi-accounts-ototals}
 \end{center}
\end{frame}
